Novelty Detection for Semantic Place Categorization

### 2011-07-15 thesis/presentation.tex

\note{
1 - A solution could pass by tagging our world with extra information, such as maps, rfids, but such a solution
is not practical and scalable.
}
\end{frame}

\begin{frame}{Problem}
\begin{block}{Machine Learning}
Give us methods to solve this problem in reverse by providing robots with knowledge
on how to detect and classify concepts and categories from the underlying sensed world.
\end{block}

@@

\subsection{Conceptual Map}
\begin{frame}{Conceptual Map}
  \begin{columns}[c]
  \column{0.5\textwidth}
    \begin{figure}
      \includegraphics[width=\textwidth]{figures/chaingraph.pdf}
    \end{figure}
  \column{0.5\textwidth}
    \begin{block}{Conceptual Map}
      The ontology is used to identify instances of the concepts and categories
      And perform probabilistic semantic mapping using graphical models.
    \end{block}
  \end{columns}

>>>>

\note{
1 - A solution could pass by tagging our world with extra information, such as maps, RFIDs, but such a solution
is not practical and scalable.
}
\end{frame}

\begin{frame}{Problem}
\begin{block}{Machine Learning}
Gives us methods to solve this problem in reverse by providing robots with knowledge
on how to detect and classify concepts and categories from the underlying sensed world.
\end{block}

@@

\subsection{Conceptual Map}
\begin{frame}{Conceptual Map}
  \begin{columns}[c]
  \column{0.5\textwidth}
    \begin{figure}
      \includegraphics[width=\textwidth]{figures/chaingraph.pdf}
    \end{figure}
  \column{0.5\textwidth}
    \begin{block}{Conceptual Map}
      The ontology is used to identify instances of the concepts and categories
      and perform probabilistic semantic mapping using graphical models.
    \end{block}
  \end{columns}
